---
title: "Exercise - 1"
output: html_notebook
author: Sena Alparslan
---

Firstly, I import data using read_csv function.

```{r}
library(readr)
dfSales <- read_csv("/Users/SENA/Desktop/EuropeanSales.csv")
dfSales
```

I check columns attributes.

```{r}
attributes(dfSales)
```

I plot correlation matric for numeric columns using corrplot. It shows between SalesPerCapita and GDPperHead is strong correlation. ComputerSalesDependant that is also our target variable, and Population is the strongest correlation of them.

```{r}
cor(dfSales[, sapply(dfSales, is.numeric)])

library(corrplot)
cor <- dfSales[, sapply(dfSales, is.numeric)]
cor <- cor[complete.cases(cor), ]
correlation_matrix <- cor(cor, method = "spearman")
corrplot(correlation_matrix, method="color")

#  SalesPerCapita  - GDPperHead 
cor(dfSales$SalesPerCapita,dfSales$GDPperHead)

#ComputerSales - Population
cor(dfSales$ComputerSales,dfSales$Population)
```

```{r}
boxplot(SalesPerCapita~GDPperHead,data=dfSales, main="SalesPerCapita/GDPperHead Box Plot",
   xlab="SalesPerCapita", ylab="GDPperHead")

library(dplyr)

filtered_data <- dfSales %>% mutate(id = row_number())
train <- filtered_data %>% sample_frac(.8) 
test  <- anti_join(filtered_data, train) 

#Stepwise using AIC --Daha iyi

null <- lm(SalesPerCapita~1, data = train)
full <- lm(SalesPerCapita ~ Population + GDPperHead + UnemploymentRate + EducationSpending + ComputerSales, data = train)

step(null, scope =list(lower=null, upper= full), direction = "both")

model_SalesPerCapita_AIC <- lm(formula = SalesPerCapita ~ GDPperHead + EducationSpending, data = train)

summary_model_1 <- summary(model_SalesPerCapita_AIC)
mse_1 <- summary_model_1$sigma^2
r_sq_1 <- summary_model_1$r.squared
adj_r_sq_1 <- summary_model_1$adj.r.squared

summary_model_1

#Stepwise using BIC

null <- lm(SalesPerCapita~1, data = train)
full <- lm(SalesPerCapita ~ Population + GDPperHead + UnemploymentRate + EducationSpending + ComputerSales, data = train)

n=dim(train[1])
step(null, scope =list(lower=null, upper= full), k=log(n), direction = "both")

model_SalesPerCapita_BIC <- lm(formula = SalesPerCapita ~ GDPperHead + Population, data = train)

summary_model_2 <- summary(model_SalesPerCapita_BIC)
mse_2 <- summary_model_2$sigma^2
r_sq_2 <- summary_model_2$r.squared
adj_r_sq_2 <- summary_model_2$adj.r.squared

summary_model_2

#Best subset regression method
library(leaps)
best_fit_model <- regsubsets (SalesPerCapita ~ Population + GDPperHead + UnemploymentRate + EducationSpending + ComputerSales,data = train,  nbest = 1, nvmax = 4)

summary(best_fit_model)

plot(best_fit_model, scale="bic")

model_SalesPerCapita_BestSubset<- lm(formula = SalesPerCapita ~ GDPperHead , data = train)

summary_model_3 <- summary(model_SalesPerCapita_BestSubset)
mse_3 <- summary_model_3$sigma^2
r_sq_3 <- summary_model_3$r.squared
adj_r_sq_3 <- summary_model_3$adj.r.squared

summary_model_3


######################################

#Stepwise using AIC

null <- lm(ComputerSales~1, data = train)
full <- lm(ComputerSales ~ Population + GDPperHead + UnemploymentRate + EducationSpending + SalesPerCapita, data = train)

step(null, scope =list(lower=null, upper= full), direction = "both")

model_ComputerSales_AIC <- lm(formula = ComputerSales ~ Population + SalesPerCapita, data = train)

summary_model_4 <- summary(model_ComputerSales_AIC)
mse_4 <- summary_model_4$sigma^2
r_sq_4 <- summary_model_4$r.squared
adj_r_sq_4 <- summary_model_4$adj.r.squared

summary_model_4

#Stepwise using BIC

n=dim(train[1])
step(null, scope =list(lower=null, upper= full), k=log(n), direction = "both")

model_ComputerSales_BIC <- lm(formula = ComputerSales ~ Population + GDPperHead + SalesPerCapita, 
    data = train)

summary_model_5 <- summary(model_ComputerSales_BIC)
mse_5 <- summary_model_5$sigma^2
r_sq_5 <- summary_model_5$r.squared
adj_r_sq_5 <- summary_model_5$adj.r.squared

summary_model_5

#Best subset regression method
library(leaps)
best_fit_model <- regsubsets (ComputerSales ~ Population + GDPperHead + UnemploymentRate + EducationSpending + SalesPerCapita,data = train,  nbest = 1, nvmax = 4)

summary(best_fit_model)

plot(best_fit_model, scale="bic")

model_ComputerSales_BEST <- lm(formula = ComputerSales ~ Population + GDPperHead + SalesPerCapita + UnemploymentRate, data = train)

summary_model_6 <- summary(model_ComputerSales_BEST)
mse_6 <- summary_model_6$sigma^2
r_sq_6 <- summary_model_6$r.squared
adj_r_sq_6 <- summary_model_6$adj.r.squared

summary_model_6

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

